Rate Transfers with Polyhedral Surrogate Losses /\\ Surrogate Regret Bounds for Polyhedral Losses

### 2021-05-21 cvx-flats-neurips21/cvx-flats.tex
flats up through setting

\begin{abstract}

  \raf{Notes}
  The prediction dimension of a surrogate is the lowest dimension $d$ such that we can construct a convex surrogate $L : \reals^d \times \Y \to \reals$ that is consistent with respect to a given prediction task.
  We present a new tool based on property elicitation to study the prediction dimension of convex surrogate loss functions.
  Our tool unifies results on prediction dimension for various settings, including continuous vs discrete predictions.
  We apply our tool in continuous estimation settings to yield a new lower bound on prediction dimension in risk measures, resolving a stated open question in the literature~\citep{frongillo2015elicitation}.
  In discrete prediction settings, this tool also recovers previous lower bounds on prediction dimension attained by feasible subspace dimension~\citep{ramaswamy2016convex}.

	\jessie{Revisit}
Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
The prediction task may be given as a target loss, as in classification and structured prediction, or simply as a (conditional) statistic of the data, as in risk measure estimation.
These two scenarios typically involve different techniques for designing and analyzing surrogate losses.
We unify these settings using tools from property elicitation, and give a general lower bound on prediction dimension which is simultaneously stronger and broader than previous results.
To understand how our framework for producing lower bounds is stronger, we introduce ``four quadrants'' of problem settings, and our bound holds for all four; previous bounds only apply to one quadrant at a time.
To demonstrate the strength of our bounds, we show new results for the prediction dimension required to estimate entropy and norms, answering an open problem of~\citet{frongillo2015elicitation}.

%Our lower bound tightens existing results in the case of discrete predictions, showing that previous calibration-based bounds can largely be recovered via property elicitation.
%For continuous estimation, our lower bound resolves an open problem on estimating measures of risk and uncertainty.
%
%
%Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
%While calibration has historically been used to reason about consistency, we propose indirect property elicitation as an alternative necessary condition for a surrogate loss to be consistent. 
%Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
%Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous calibration-based bounds can largely be recovered purely via property elicitation.
%For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
\end{abstract}

@@

% examples of problems where we care a lot about prediction dimension (that happen to be finite discrete)
Despite the ubiquity of surrogate losses, we lack general frameworks to design and analyze consistent surrogates.
This state of affairs is especially dire when one seeks low \emph{prediction dimension}, the dimension of the surrogate prediction domain.
For example, in multiclass classification with $n$ labels, the prediction domain might be $\reals^n$.
In many type (I) settings, such as structured prediction and extreme classification, the prediction dimension can easily become intractably large, forcing one to sacrifice consistency for computational efficiency.
To understand whether this sacrifice is necessary, recent work developed tools like the feasible subspace dimension to lower bound the prediction dimension of any consistent convex surrogate~\citep{ramaswamy2016convex}.
Challenges of type (II) include risk measures such as conditional value at risk (CVaR), with applications in financial regulation, robust engineering design, and algorithmic fairness.
Risk measures provably cannot be specified via a \jessiet{discrete? this sentence confuses me as is because the surrogate could be the target?} target loss, and thus we seek a surrogate loss of low (or at least finite) prediction dimension.
Recent work~\citep{fissler2016higher,frongillo2020elicitation} gives prediction dimension bounds for some of these risk measures, but without the requirement that the surrogate be convex: bounds for convex surrogates are left as a major open question.

@@

\paragraph{The ``four quadrants'' of problem types}
Above, we discuss a significant divergence in previous frameworks: constructing a surrogate given a \emph{target loss} versus a \emph{target statistic}.
In addition to the two possible targets, we may have one of two domains: a \emph{discrete} (i.e.\ finite) target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
We informally refer to the four resulting cases---target loss vs.\ target statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems, shown in Table~\ref{tab:quadrants}.
For further examples, see Appendix~\ref{app:omitted-examples}.
In the context of these quadrants, Figure~\ref{fig:results-flow} gives a roadmap of our main results.

\paragraph{Literature on consistency and calibration}% \label{subsec:consistency}
%\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
%\jessiet{Make this subsection more concise?}
We focus on the construction of consistent surrogate losses $L: \reals^d \times \Y \to \reals$, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.
When given a \emph{target loss} $\ell$, we roughly define $L$ to be consistent if minimizing $L$, and applying a link function, minimizes $\ell$ (Definition \ref{def:consistent-ell} in Appendix~\ref{sec:consis-implies-indir})~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
When given a target statistic such as the conditional quantile or variance, but no target loss, we introduce a notion of consistency in line with classical statistics (Definition \ref{def:consistent-prop} in Appendix~\ref{sec:consis-implies-indir}) \citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct statistic value.

\jessiet{Do we still want this following paragraph?}
A priori, it is not clear that compatible definitions of consistency could be given for both target statistics and target losses.
In fact, we observe that consistency for target losses is a special case of consistency for target statistics (\S~\ref{sec:consis-implies-indir}).
This observation suggests property elicitation (see \S~\ref{subsec:properties}) as a useful tool to study general lower bounds.
%Most prior work on convex consistency dimension focuses on problems in Quadrant 1~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.

As definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration, which only applies when given a target loss, e.g. Quadrants 1 and 3. 
Particularly,~\citet{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in Quadrant 1, where one is given a target statistic and discrete prediction set.
We discuss the additional relationship of elicitation and calibration in Appendix~\ref{app:calibration}, and derive Theorem~\ref{thm:consistent-implies-indir-elic} via calibration.

@@

\begin{table}[t]
	\begin{center}
	\begin{tabular}{p{12ex}|l|l|} 
		& \emph{Target loss}  & \emph{Target statistic}\\ \hline
		\emph{Discrete} & \textbf{Q1:} Classification  & \textbf{Q2:} Risk-averse classification\\ 
		{\em prediction} & & (Appendix~\ref{app:omitted-examples})\\ \hline 
		\emph{Continuous } & \textbf{Q3:} Least-squares regression & \textbf{Q4:} Variance estimation\\ 
		\emph{estimation}& & \\
		\hline
	\end{tabular}
\caption{The four quadrants of problem types, with an example of interest for each.}
\label{tab:quadrants}
\end{center}
\end{table}

@@

\draw[edge] (d-flats) to node[above, sloped]{Cor.~\ref{cor:Pcodim-flat-elic-relint-prop}} (q4-bounds);
\draw[edge] (d-flats) to node[above, sloped]{Cor.~\ref{cor:Pcodim-flat-single-val-prop}} (q1-bounds);
\end{tikzpicture}
}
\end{center}
\caption{\raf{Problem: ref quadrants before defining them, but don't want type I and II either}
  Flow and implications of our results. Compared to calibration, we suggest indirect elicitation as a simpler but almost-as-powerful necessary condition for consistency. In particular, we obtain a testable necessary condition, based on $d$-flats, for whether there exists a $d$-dimensional consistent convex surrogate. This condition recovers and strengthens existing calibration-based results.}
\label{fig:results-flow}
\end{figure}

@@

If given, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss}, with predictions $r\in\R$.
%where the goal is minimize expected loss, $\E ~ \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_{Y \sim p} L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, that are minimizable in that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex (in $\reals^d$ for every $y \in \Y$) losses in $\L_d$.
\btw{Sufficient condition for $\A$-normal convex integrand: $L$ is lower semi-continuous and $\mathcal{B}(\A) \otimes \Y$-measurable; $\E_p L(u,Y)$ finite for all $u, p$, there exists a $u_0$ for each $p$ so that $\E_p L(u_0, Y)$ is finite and continuous for Rockefellar's corollary, though it's stricter than Ioffe and Tokhimorov IIRC}
%Similarly, let $\L_d^{fin}$ be surrogates $L: \reals^d \times \Y \to \reals$ that are $\mathcal{B}(\reals^d) \otimes \Y$-measurable and minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$-- we use this class of losses with finite $\Y$ in mind.
Set $\L = \cup_{d \in \mathbb{N}} \L_d$, and $\Lcvx = \cup_{d \in \mathbb{N}} \Lcvx_d$.
A loss $\ell: \R\times \Y \to \reals$ is \emph{discrete} if $\R$ is a finite set.
%A surrogate $L:\reals^d \times \Y \to \reals$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ almost surely in $\Y$.
\jessiet{Need this?}
For a given $p\in\P$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
Typically, we notate finite report sets $\R$.

@@

\subsection{Property elicitation}\label{subsec:properties}
\jessiet{This sentence might make me wary of minnability assumptions as a reviewer}
Arising from the statistics and economics literature, property elicitation is similar to calibration, but only characterizes exact minimizers of a surrogate~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,lambert2009eliciting,lambert2018elicitation,frongillo2015vector-valued,frongillo2014general}.
Specifically, given a statistic or \emph{property} $\Gamma$ of interest, which maps a distribution $p \in \P \subseteq \simplex$ to the set of desired or correct predictions, the minimizers of $L$ should precisely coincide with $\Gamma$.
For example, squared loss $L(r,y) = (r-y)^2$ elicits the mean $\Gamma(p) = \E_p Y$.
For intuition, to relate to consistency, one can think of $p = \Pr[Y|X=x]$ as a conditional distribution, though the definition is also applied to point prediction settings.

@@

While implicitly observed in some of the literature~\citep{steinwart2008support}\jessie{Add more}, we can observe that consistency implies indirect elicitation.
Formal definitions and the following proof are deferred to Appendix~\ref{sec:consis-implies-indir}, but consistency loosely mean that converging to the optimal surrogate loss in expectation over the data distribution $\D \sim \X \times \Y$ implies that we can apply a link to the convergent sequence and approach the optimal target loss in expectation or conditional statistical value.

@@

An important caveat to the above elicitation definitions is that, since $\Gamma = \prop[\P]{L}$ is nonempty everywhere, we must have $L\in\L$, meaning that $\exploss{L}{\cdot}{p}$ always achieves a minimum.
This restriction is also implicit in e.g.~\citep{agarwal2015consistent}.
While some popular surrogates such as logistic and exponential loss are not minimizable, these losses are still covered in Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} and Theorem~\ref{thm:bayes-risk-lower-bound} as $\Gamma(p) \neq \emptyset$ when $p\in\P := \relint\simplex$; moreover, by thresholding $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$ we can achieve $L'\in\L$ for both.
We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray), thereby ensuring a minimum is always achieved for convex losses, would allow us to lift the minimizable restriction entirely.
\btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}

@@

\begin{definition}[Convex Consistency Dimension]\label{def:cvx-consistency-dim}
  Given target loss $\ell:\R \times\Y \to \reals$ or property $\gamma: \P \toto \R$, its \emph{convex consistency dimension} $\conscvx(\cdot)$ is the minimum dimension $d$ such that $\exists L \in \Lcvx_d$ and link $\psi$ such that $(L,\psi)$ is consistent with respect to $\ell$ or $\gamma$.
%	\btw{Maybe take out of definition environment, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
\end{definition}
\jessiet{Cut this sentence?  Lots of refs to it}
\emph{Consistency} is defined for a target loss in Definition~\ref{def:consistent-ell} and for a target property in Definition~\ref{def:consistent-prop} in Appendix~\ref{sec:consis-implies-indir}.

@@

\subsection{Illustration: geometric intuition for the four quadrants}
We can apply Lemma~\ref{lem:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants by Corollaries~\ref{cor:Pcodim-flat-single-val-prop} (for continuous estimation problems; Q3, Q4) and~\ref{cor:Pcodim-flat-elic-relint-prop} (for discrete prediction problems; Q1, Q2).
The illustrations in Table~\ref{tab:quadrants-simplices} are simply intended to show how Lemma~\ref{lem:convex-flats-inf-dim} can be applied to results in all four quadrants of problem types-- making it the first lower bound to our knowledge to do so.

>>>>

\begin{abstract}
The prediction dimension of a supervised learning task is the lowest dimension $d$ such that there exists a convex surrogate $L : \mathbb{R}^d \times \mathcal{Y} \to \mathbb{R}$ that is consistent for the given task.
  We present a new tool based on property elicitation, $d$-flats, for lower-bounding prediction dimension.
  This tool unifies approaches from a variety of domains, including continuous and discrete prediction problems.
  We use $d$-flats to obtain a new lower bound on the prediction dimension of risk measures, addressing an open question due to Frongillo and Kash (NeurIPS 2015).
  In discrete prediction settings, we show that the $d$-flats approach recovers and even tightens previous lower bounds using feasible subspace dimension.
\end{abstract}

@@

% examples of problems where we care a lot about prediction dimension (that happen to be finite discrete)
Despite the ubiquity of surrogate losses, we lack general frameworks to design and analyze consistent surrogates.
This state of affairs is especially dire when one seeks low \emph{prediction dimension}, the dimension of the surrogate prediction domain.
For example, in multiclass classification with $n$ labels, the prediction domain might be $\reals^n$.
In many type (I) settings, such as structured prediction and extreme classification, the prediction dimension can easily become intractably large, forcing one to sacrifice consistency for computational efficiency.
To understand whether this sacrifice is necessary, recent work developed tools like the feasible subspace dimension to lower bound the prediction dimension of any consistent convex surrogate~\citep{ramaswamy2016convex}.
Challenges of type (II) include estimating risk measures such as conditional value at risk (CVaR), with applications in financial regulation, robust engineering design, and algorithmic fairness.
Risk measures are not elicitable, meaning they cannot be specified via a \jessiet{discrete? this sentence confuses me as is because the surrogate could be the target?}\raft{better?} target loss, and thus we seek a surrogate loss of low (or at least finite) prediction dimension.
Recent work~\citep{fissler2016higher,frongillo2020elicitation} gives prediction dimension bounds for some of these risk measures, but without the requirement that the surrogate be convex; bounds for convex surrogates are left as a major open question.

@@

\paragraph{The ``four quadrants'' of problem types.}
Above, we discuss a significant divergence in previous frameworks: constructing a surrogate given a \emph{target loss} versus a \emph{target statistic}.
In addition to the two possible targets, we may have one of two domains: a \emph{discrete} (i.e.\ finite) target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
We informally refer to the four resulting cases---target loss vs.\ target statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems, shown in Table~\ref{tab:quadrants}.
% For further examples, see Appendix~\ref{app:omitted-examples}.
In the context of these quadrants, Figure~\ref{fig:results-flow} gives a roadmap of our main results.

\paragraph{Literature on consistency and calibration.}% \label{subsec:consistency}
%\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
%\jessiet{Make this subsection more concise?}
We focus on consistent surrogate losses $L: \reals^d \times \Y \to \reals$, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.
When given a \emph{target loss} $\ell$, we roughly define $L$ to be consistent if minimizing $L$, and applying a link function, minimizes $\ell$ (Def.~\ref{def:consistent-ell}, \S~\ref{sec:consis-implies-indir})~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
When given a target statistic such as the conditional quantile or variance, but no target loss, we introduce a notion of consistency in line with classical statistics (Def.~\ref{def:consistent-prop}, \S~\ref{sec:consis-implies-indir}) \citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct statistic value.

\jessiet{Do we still want this following paragraph?}
\raft{Good question.  I edited a bit, but still up for discussion.}
A priori, it is not clear that compatible definitions of consistency could be given for both target statistics and target losses.
In fact, a key observation which underpins our approach is that consistency for target losses is a special case of consistency for target statistics (\S~\ref{sec:consis-implies-indir}), suggesting property elicitation (see \S~\ref{subsec:properties}) a useful tool to study general lower bounds.
%Most prior work on convex consistency dimension focuses on problems in Quadrant 1~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.

As definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called \emph{calibration}, which only applies when given a target loss, e.g. Quadrants 1 and 3. 
Particularly, several authors~\citep{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in Quadrant 1, where one is given a target statistic and discrete prediction set.
We discuss the additional relationship of elicitation and calibration in Appendix~\ref{app:calibration}, and derive Theorem~\ref{thm:consistent-implies-indir-elic} via calibration.

@@

% \begin{tabular}{lcccccl}\toprule
% & \multicolumn{3}{c}{$\tol=\tols$} & \multicolumn{3}{c}{$\tol=\told$}
% \\\cmidrule(lr){2-4}\cmidrule(lr){5-7}
%            & $mv$  & Rel.~err & Time    & $mv$  & Rel.~err & Time\\\midrule
% \trigmv    & 11034 & 1.3e-7 & 3.9 & 15846 & 2.7e-11 & 5.6 \\
% \trigexpmv & 21952 & 1.3e-7 & 6.2 & 31516 & 2.7e-11 & 8.8 \\
% \trigblock & 15883 & 5.2e-8 & 7.1 & 32023 & 1.1e-11 & 1.4e1\\
% \expleja   & 11180 & 8.0e-9 & 4.3 & 17348 & 1.5e-11 & 6.6 \\\bottomrule
% \end{tabular}

\begin{table}[t]
  \begin{center}
    \aboverulesep=1ex
    \belowrulesep=1ex
    \begin{tabular}{p{12ex}ll}
      & \emph{Target loss}  & \emph{Target statistic}\\
      \cmidrule[1pt]{2-3}
      \parbox{12ex}{\emph{Discrete \\ prediction}} & \textbf{Q1:} Classification  & \textbf{Q2:} Risk-averse classification\\ 
      \cmidrule{2-3}
      \parbox{12ex}{\emph{Continuous \\ estimation}} & \textbf{Q3:} Least-squares regression & \textbf{Q4:} Variance estimation\\ 
      \cmidrule[1pt]{2-3}
      \\
    \end{tabular}
    \caption{The four quadrants of problem types, with an example for each as discussed in \S~\ref{sec:illustration}.}
    \label{tab:quadrants}
  \end{center}
\end{table}

@@

\draw[edge] (d-flats) to node[above, sloped]{Cor.~\ref{cor:Pcodim-flat-elic-relint-prop}} (q4-bounds);
\draw[edge] (d-flats) to node[above, sloped]{Cor.~\ref{cor:Pcodim-flat-single-val-prop}} (q1-bounds);
\end{tikzpicture}
}
\end{center}
\caption{Flow and implications of our results. Compared to calibration, we suggest indirect elicitation as a simpler but almost-as-powerful necessary condition for consistency. In particular, we obtain a testable necessary condition, based on $d$-flats, for whether there exists a $d$-dimensional consistent convex surrogate. This condition recovers and strengthens existing calibration-based results.}
\label{fig:results-flow}
\end{figure}

@@

If given, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss}, with predictions $r\in\R$.
%where the goal is minimize expected loss, $\E ~ \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_{Y \sim p} L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, that are minimizable in that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex (in $\reals^d$ for every $y \in \Y$) losses in $\L_d$.
\btw{Sufficient condition for $\A$-normal convex integrand: $L$ is lower semi-continuous and $\mathcal{B}(\A) \otimes \Y$-measurable; $\E_p L(u,Y)$ finite for all $u, p$, there exists a $u_0$ for each $p$ so that $\E_p L(u_0, Y)$ is finite and continuous for Rockefellar's corollary, though it's stricter than Ioffe and Tokhimorov IIRC}
%Similarly, let $\L_d^{fin}$ be surrogates $L: \reals^d \times \Y \to \reals$ that are $\mathcal{B}(\reals^d) \otimes \Y$-measurable and minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$-- we use this class of losses with finite $\Y$ in mind.
Set $\L = \cup_{d \in \mathbb{N}} \L_d$, and $\Lcvx = \cup_{d \in \mathbb{N}} \Lcvx_d$.
A loss $\ell: \R\times \Y \to \reals$ is \emph{discrete} if $\R$ is a finite set.
%A surrogate $L:\reals^d \times \Y \to \reals$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ almost surely in $\Y$.
\jessiet{Need this?}
\raft{Assuming you mean regret -- no I think we can move to the appendix now, for consistency stuff}
For a given $p\in\P$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
Typically, we notate finite report sets $\R$.

@@

\subsection{Property elicitation}\label{subsec:properties}
\jessiet{This sentence might make me wary of minnability assumptions as a reviewer}
\raft{True, but we address it below.  We could forward reference that discussion.  I think it's okay though.}
Arising from the statistics and economics literature, property elicitation is similar to calibration, but only characterizes exact minimizers of a surrogate~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,lambert2009eliciting,lambert2018elicitation,frongillo2015vector-valued,frongillo2014general}.
Specifically, given a statistic or \emph{property} $\Gamma$ of interest, which maps a distribution $p \in \P \subseteq \simplex$ to the set of desired or correct predictions, the minimizers of $L$ should precisely coincide with $\Gamma$.
For example, squared loss $L(r,y) = (r-y)^2$ elicits the mean $\Gamma(p) = \E_p Y$.
For intuition, to relate to consistency, one can think of $p = \Pr[Y|X=x]$ as a conditional distribution, though the definition is also applied to point prediction settings.

@@

As observed implicitly and explicitly in the literature, e.g.~\citep{steinwart2008support,agarwal2015consistent}, the following proposition states that consistency implies indirect elicitation.
Informally, consistency means that a hypothesis sequence converging to the optimal surrogate loss, in expectation over the data distribution $\D \sim \X \times \Y$, links to a sequence converging to the optimal target loss or conditional statistical value.
See \S~\ref{sec:consis-implies-indir} for definitions and the proof.

@@

Implicit in the above elicitation definitions is that $L\in\L$, meaning $L$ is minimizable: since $\Gamma = \prop[\P]{L}$ is nonempty everywhere, the expected loss $\exploss{L}{\cdot}{p}$ always achieves a minimum.
This restriction is also implicit in previous work, e.g.,~\citep{agarwal2015consistent}.
While some popular surrogates such as logistic and exponential loss are not minimizable, these losses are still covered in Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} and Theorem~\ref{thm:bayes-risk-lower-bound} as $\Gamma(p) \neq \emptyset$ when $p\in\P := \relint\simplex$; moreover, by thresholding $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$ we can achieve $L'\in\L$ for both.
We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray) would allow us to assume minimizability without loss of generality, as convex losses would always admit this more general minimizer.
\btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}

@@

\begin{definition}[Convex Consistency Dimension]\label{def:cvx-consistency-dim}
  Given target loss $\ell:\R \times\Y \to \reals$ or property $\gamma: \P \toto \R$, its \emph{convex consistency dimension} $\conscvx(\cdot)$ is the minimum dimension $d$ such that $\exists L \in \Lcvx_d$ and link $\psi$ such that $(L,\psi)$ is consistent with respect to $\ell$ or $\gamma$.
%	\btw{Maybe take out of definition environment, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
\end{definition}
% \jessiet{Cut this sentence?  Lots of refs to it}
% \emph{Consistency} is defined for a target loss in Definition~\ref{def:consistent-ell} and for a target property in Definition~\ref{def:consistent-prop} in Appendix~\ref{sec:consis-implies-indir}.

@@

\subsection{Illustration: geometric intuition for the four quadrants}
\label{sec:illustration}
We can apply Lemma~\ref{lem:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants by Corollaries~\ref{cor:Pcodim-flat-single-val-prop} (for continuous estimation problems; Q3, Q4) and~\ref{cor:Pcodim-flat-elic-relint-prop} (for discrete prediction problems; Q1, Q2).
The illustrations in Table~\ref{tab:quadrants-simplices} are simply intended to show how Lemma~\ref{lem:convex-flats-inf-dim} can be applied to results in all four quadrants of problem types-- making it the first lower bound to our knowledge to do so.

### 2021-05-21 rates-neurips-21/rates.tex
flats up through setting

\begin{abstract}
  Surrogate risk minimization is an ubiquitous paradigm in supervised machine learning, wherein a target problem is solved by minimizing a surrogate loss on a dataset.
  Surrogate regret bounds are a common tool to prove generalization rates for surrogate risk minimization.
  While surrogate regret bounds have been developed for certain classes of loss functions, such as proper losses, general results are relatively sparse.
  We provide two general results.
  The first gives a linear surrogate regret bound for any polyhedral (piecewise-linear convex) surrogate, meaning that surrogate generalization rates translate directly to target rates.
  The second shows that for ``non-polyhedral'' surrogates, the regret bound is a square root, meaning fast surrogate generalization rates translate to slow rates for the target.
  Together, these results suggest polyhedral surrogates are weakly optimal in many cases.
\end{abstract}

>>>>

\begin{abstract}
  Surrogate risk minimization is an ubiquitous paradigm in supervised machine learning, wherein a target problem is solved by minimizing a surrogate loss on a dataset.
  Surrogate regret bounds are a common tool to prove generalization rates for surrogate risk minimization.
  While surrogate regret bounds have been developed for certain classes of loss functions, such as proper losses, general results are relatively sparse.
  We provide two general results.
  The first gives a linear surrogate regret bound for any polyhedral (piecewise-linear convex) surrogate, meaning that surrogate generalization rates translate directly to target rates.
  The second shows that for sufficiently non-polyhedral surrogates, the regret bound is a square root, meaning fast surrogate generalization rates translate to slow rates for the target.
  Together, these results suggest polyhedral surrogates are weakly optimal in many cases.
\end{abstract}
